\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

%%%-----------------------------------------------------------------
%
\subsection{Testing with natural-like textures}
%%%-----------------------------------------------------------------
To test our model, we will quantify its ability to categorize different motions, that is on event streams for which the ground truth motion is known at every instant in time. Before applying the model on natural images, we will first test the model on simpler, parameterized stimuli. In that order, we use a set of synthetic visual stimuli, \textit{Motion Clouds}~\citep{leon_motion_2012} which are natural-like random textures for which we can control for velocity, among other parameters (\seeFig{motion_clouds})~\citep{vacher_bayesian_2018}. In particular, we will set the spatial size and duration similarly to the motion task defined above. 
This procedure defines a set of textures with different spatial properties and different motions $\va{v}_k$ with  $1 \le k \le \Nclass$ and $\Nclass=8$ defined by a constant speed and linearly spaced directions $
\speed_\kernelind = 
  ( 
    \speed \cdot \cos(2\pi\cdot \frac{\kernelind}{\Nspeed}),
    \speed \cdot \sin(2\pi\cdot \frac{\kernelind}{\Nspeed})
  )
$.
For any given velocity, we also varied the parameters of the textures, such as the mean and variance of the orientation or spatial frequency content to provide with some naturalistic variability. This method provides a rich dataset of textured movies for which we know the ground truth for motion.
%%%-----------------------------------------------------------------
%: fig:motion_clouds
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.99\linewidth]{figures/motion_clouds.pdf} %
    \caption{{\bf Role of stimulus parameters in the motion detection accuracy.} Accuracy as a function of (from left to right) the mean spatial frequency, the bandwidth in orientation (from a grating-like (left) to isotropic textures (right)), the bandwidth in spatial frequency, the bandwidth in speed, from a rigid motion (left) to independent frames (right). Note that these accuracy is computed both in the case where orientation of the synthetic texture is necessarily perpendicular to the motion ('no aperture' condition) or in the arbitrary case where orientation is independent of direction ('aperture').}
    \label{fig:motion_clouds}
\end{figure}
%%%-----------------------------------------------------------------

We plot here main axis of interests. First, as we change the mean spatial frequency of the texture, we observe a monotonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{priebe_tuning_2006}. %\note{we should really do something more serious here...} 
Notably, the accuracy is better for a large spatial frequency bandwidth (which qualitatively resemble a more textured stimulus) than for a grating-like stimulation, reminiscent to the behavioral response of humans' eye movements to such stimuli~\citep{simoncini_more_2012}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy, similar to that observed in the amplitude of humans' eye movements~\citep{mansour_pour_speed_2018} but also that accuracy is low for a rigid motion which lacks variability.
%
\subsection{Accuracy efficiency trade-off}% for the motion detection task}
%%%-----------------------------------------------------------------
Once our MLR is trained, we obtain spatio-temporal kernels corresponding to the weights associated to the heterogeneous delays of our layer of spiking neurons and which may be used for detection. We observed that the distribution of the kernels' weights is sparse, with most values near zero. As shown in the formalization of our event-based model, the computational cost of our model if implemented on a neuromorphic chip would be dominated by the number of spikes times the number of synapses. Indeed, the computations are dominated by the convolution operation. In a dense setting, this corresponds for all voxels in the output to a sum over all voxels in the inputs for all weights in the kernel. If the support of information is sparse, then computations can be performed only on those events. Also, if we set some weights of the kernels to zero, then the sum can be skipped for those addresses. Knowing the sparseness of the input, the total number of computations thus scales with the number of nonzero synaptic weights.

>>>>

%%%-----------------------------------------------------------------
%
\subsection{Testing with natural-like textures}
%%%-----------------------------------------------------------------
To test our model, we will quantify its ability to categorize different motions, that is on event streams for which the ground truth motion is known at every instant in time. Before applying the model on natural images, we will first test the model on simpler, parameterized stimuli. In that order, we use a set of synthetic visual stimuli, \textit{Motion Clouds}~\citep{leon_motion_2012} which are natural-like random textures for which we can control for velocity, among other parameters (\seeFig{motion_clouds})~\citep{vacher_bayesian_2018}. In particular, we will set the spatial extent and duration of the generated movies similarly to the motion task defined above. This procedure defines a set of textures with different spatial properties and different motions picked from the same set of $8$ directions and $3$ speeds. For any given velocity, we also varied the parameters of the textures, such as the mean and variance of the orientation or spatial frequency content to provide with some naturalistic variability. This method provides a rich dataset of textured movies for which we know the ground truth for motion.
%%%-----------------------------------------------------------------
%: fig:motion_clouds
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.99\linewidth]{figures/motion_clouds.pdf} %
    \caption{{\bf Role of stimulus parameters in the motion detection accuracy.} Accuracy as a function of (from left to right) the mean spatial frequency, the bandwidth in orientation (from a grating-like (left) to isotropic textures (right)), the bandwidth in spatial frequency, the bandwidth in speed, from a rigid motion (left) to independent frames (right). Note that these accuracy is computed both in the case where orientation of the synthetic texture is necessarily perpendicular to the motion ('no aperture' condition) or in the arbitrary case where orientation is independent of direction ('aperture').}
    \label{fig:motion_clouds}
\end{figure}
%%%-----------------------------------------------------------------

We plot here main axis of interests. First, as we change the mean spatial frequency of the texture, we observe a monotonous decrease in accuracy. This comes as a similar trend as that observed in the primary visual areas~\citep{priebe_tuning_2006} and revels the most informative scales learned by our model. We observe the tendency for different spatial frequency bandwidth. Notably, the accuracy is better for a large (which qualitatively resemble a more textured stimulus) than , reminiscent to the behavioral response of humans' eye movements to such stimuli~\citep{simoncini_more_2012}. Interestingly, we also see a modulation of accuracy as a function of orientation bandwidth. When the stimulus is grating-like and that the orientation is arbitrary with respect to the direction of motion, the system is faced with the aperture problem and see a decrease of accuracy. This is not the case for isotropic stimuli or when the orientation is perpendicular to the direction of motion. Finally, we manipulated the amount of change between two successive frames, similar to a temperature parameter. This shows a progressive decrease in accuracy, similar to that observed in the amplitude of humans' eye movements~\citep{mansour_pour_speed_2018} but also that accuracy is low for a rigid motion which lacks variability.
%
\subsection{Accuracy efficiency trade-off}% for the motion detection task}
%%%-----------------------------------------------------------------
Once our MLR is trained, we obtain spatio-temporal kernels corresponding to the weights associated to the heterogeneous delays of our layer of spiking neurons and which may be used for detection. We observed that the distribution of the kernels' weights is sparse, with most values near zero. As shown in the formalization of our event-based model, the computational cost of our model if implemented on a neuromorphic chip would be dominated by the number of spikes times the number of synapses. Indeed, the computations are dominated by the convolution operation. In a dense setting, this corresponds for all voxels in the output to a sum over all voxels in the inputs for all weights in the kernel. If the support of information is sparse, then computations can be performed only on those events. Also, if we set some weights of the kernels to zero, then the sum can be skipped for those addresses. Knowing the sparseness of the input, the total number of computations thus scales with the number of nonzero synaptic weights.
